Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-03 ECCV/paper.tex
dummy change.

\subsection{Fiducial Detection Algorithm}
Apply Gabor Filter on input image \\
Find Connected components in Gabor output \\
Cluster the connected components \\
Merge the clusters \\
Detect code in the bounding box \\
Classify the detected code

>>>>

\subsection{Fiducial Detection Algorithm}
Apply Gabor Filter on input image \\
Find Connected components in Gabor output \\
Cluster the connected components \\
Merge the clusters \\
Detect code in the bounding box \\
Classify the detected code by the classifer trained on standards.
